\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

This paper estimates the causal impact of migrant remittances on child
multidimensional poverty in Senegal using two rounds of the Harmonized
Household Living Standards Survey (EHCVM I, 2018-2019 and EHCVM II, 2021-2022).
The identification strategy combines propensity score matching (PSM) and
difference-in-differences (PSM-DiD estimator of Heckman et al., 1997-1998),
simultaneously addressing selection bias on observables and time-invariant
unobservable fixed effects.

Child multidimensional poverty is measured primarily using the N-MODA approach
(7 dimensions, threshold $k=4$, age groups 0-4, 5-14 and 15-17 years), with
the Alkire-Foster method as a robustness check (6 indicators, threshold $k=1/3$,
equal weights). In 2018-2019, the incidence of child multidimensional poverty
reaches 58.9\% under N-MODA and 62.0\% under the AF approach, declining to
51.6\% and 56.3\% respectively by 2021-2022.

The PSM-DiD estimator yields an ATT of $+0.027$ ($p = 0.512$) for the
N-MODA incidence and $+0.023$ ($p = 0.599$) for the Alkire-Foster incidence.
After correcting for selection bias, remittances have no statistically significant
overall effect on child multidimensional poverty. This null result is robust
to the choice of matching algorithm (k-nearest neighbors, Epanechnikov kernel,
caliper) and to the inter-dimensional threshold $k$.

Disaggregation by dimension reveals one significant effect: children in
recipient households have a 4.3 percentage point lower probability of
educational deprivation (ATT $= -0.043$, $p = 0.041$), consistent with
households prioritizing investment in children's schooling. No significant
effects are found for the remaining six dimensions (sanitation, water, housing,
nutrition, health, child protection).

These findings suggest that remittances to Senegal have not yet reached the
critical mass required to reduce structural child poverty across multiple
dimensions, and point to the need for policies combining lower remittance
transaction costs with stronger complementarity between private transfers and
public services, particularly in education.

\bigskip

\noindentKeywords: child multidimensional poverty, N-MODA, remittances,
Senegal, EHCVM, propensity score matching (PSM), difference-in-differences (DiD),
Alkire-Foster.
